% Created 2021-01-18 Mon 17:40
\documentclass[Ingles]{ic-tese-v3}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\date{}
\title{}
\hypersetup{
 pdfauthor={Laura Viglioni},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.1 (Org mode 9.4.3)}, 
 pdflang={English}}
\begin{document}

\autora{Laura Viglioni}

\title{The Dissertation or Thesis Title in English}

\orientador{Prof. Dr. Ricardo Dahab}

\mestrado

\datadadefesa{22}{04}{1500}

\paginasiniciais

\chapter{Introduction}
\label{sec:org1d79cb0}

\chapter{Mathematical Background}
\label{sec:org3d5629b}

\section{Groups}
\label{sec:org7f3a9d3}

   \begin{definition}
  A \textbf{group} is a set $G$ closed under a binary operation $\cdot$ defined on $G$ such
  that:
  \begin{itemize}
  \item \textbf{Associativity: } $\forall a,b,c \in G, \; a\cdot(b\cdot c) = (a\cdot b)\cdot c$
  \item \textbf{Identity element: } $\exists e \in G \; ; \; \forall a \in G, \; a\cdot e = e\cdot a = a$
  \item \textbf{Inverse element: } $\forall a \in G, \; \exists b \in G \; ; \; a\cdot b = b \cdot a = e$
  \end{itemize}
And it is denoted by $\langle G,\cdot\rangle$, or simply $G$ if the operation is implied.
\end{definition}

\begin{definition}
  A group is said to be \textbf{commutative} or \textbf{abelian}
  if $\forall a, b \in G, \; a\cdot b = b\cdot a$
\end{definition}

\noindent
A group is called \textbf{additive} or \textbf{multiplicative} if its
operation is addition or multiplication, respectively.

\begin{definition}
  A subset $H$ of $G$ is a \textbf{subgroup} of $\langle G,\cdot \rangle$ if it is
  closed under $\cdot$ induced by $\langle G,\cdot \rangle$.
\end{definition}

\begin{definition}
  The \textbf{order} of a group $\langle G,\cdot\rangle$ is the cardinality of the set $G$.
\end{definition}

\begin{definition}
  A subgroup $H$ of $G$ can be used to decompose $G$ in uniform sized and
  disjoints subsets called \textbf{cosets}. Given an element $g \in G$:
  \begin{itemize}
  \item A \textbf{left coset} is defined by $gH := \{g\cdot h \; ; \; h \in H\}$
  \item A \textbf{right coset} is defined by $Hg := \{h\cdot g \; ; \; h \in H\}$
  \end{itemize}
\end{definition}

\section{Rings and Fields}
\label{sec:org53d70b3}

   \begin{definition}
  A \textbf{ring} is a set together with two binary operations, we will note by
  $+$ and $*$ and call it addition and multiplication, respectively, such that:
  \begin{itemize}
  \item $\langle R,+\rangle$ is an abelian group.
  \item $*$ is associative
  \item $*$ is distributive over $+$
  \end{itemize}

  And it is denoted by $\langle R,+,*\rangle$, or simply $G$ if the operations are implied.
\end{definition}

\begin{definition}
  A ring is said to be \textbf{commutative} if its $*$ operation is commutative.
\end{definition}

\begin{definition}
  A ring is said to be \textbf{with unity} if $*$ has a identity element. We
  shall note it by $1$ and it is called \textbf{unity}.

\end{definition}

\begin{definition}
  A \textbf{division ring} is a ring R where $\forall r \in R, \; \exists s \in R \; ; \; r*s = 1$.
\end{definition}

\begin{definition}
  A \textbf{field} is a commutative division ring.
\end{definition}

\section{Lattices}
\label{sec:orgd1564bb}

   \begin{definition}
  A Lattice $\Lambda \subset \mathbb{R}^n$ is a subgroup of the additive group $\mathbb{R}^n$
\end{definition}

In other words, given \(m\) linear independent vectors in \(\mathbb{R}^n\), the set
\(\{v_1, v_2, ..., v_m\}\) is called a \textbf{basis} for \(\Lambda\) and the Lattice may defined
by:

\begin{definition}
  \begin{equation}
    \Lambda := \left\{x = \sum_{i=1}^m{\lambda_iv_i} \in \mathbb{R}^n \; | \; \lambda_i \in \mathbb{Z}\right\}
  \end{equation}
\end{definition}

\section{Number Fields}
\label{sec:org4ba9301}

   \begin{definition}
  Let $K$ and $L$ be two fields, $L$ is said to be a \textbf{field extension} of
  $K$ if $L \subseteq K$ and we denote it by $L/K$
\end{definition}

Note that in a field extension \(L/K\), \(L\) has a structure of a vector space over
\(K\), where vector addition is in \(L\) and scalar multiplication \(a \in K, \; v \in L
\; \implies av \in L\). The dimension of \(L\) as a vector space is called
\textbf{degree} and it is denoted by \([L:K]\).

\begin{definition}
  A field extension is called \textbf{number field} when it is over $\mathbb{Q}$.
\end{definition}

\begin{definition}
  Let $\alpha \in L$ where $L/K$ is a field extension. We say that $\alpha$ is
  \textbf{algebraic over $K$} if $\exists p \in K[X] \;;\; p(\alpha) = 0$. $p$ is said to be
  \textbf{the minimal polynomial of $\alpha$ over $K$} denoted by $p_\alpha$. If $\alpha \in L =
  \mathbb{Q}[\theta]$, we simply call $\alpha$ an \textbf{algebraic number}.
\end{definition}

\begin{example}
  It is known that $\mathbb{Q}$ is a field. If we add $\sqrt{2}$ to the set, we
  can build a new field adding also all the powers and multiples of
  $\mathbb{Q}$. This new field is denoted by $\mathbb{Q}[\sqrt{2}]$, note that
  $\sqrt{2}$ is algebraic and its minimal polynomial $p_{\sqrt{2}} = x^2-2$. All
  elements of $\mathbb{Q}[\sqrt{2}]$ are in the form $\{a+b\sqrt{2} \;|\; a,b \in
  \mathbb{Q}\}$ and one of its basis is $\{1, \sqrt{2}\}$, so it has degree is
  $2$.
\end{example}

\begin{example}
  If we add $\sqrt[3]{2}$ to $\mathbb{Q}$ instead, its elements would have the
  form $\{a + b\sqrt[3]{2} + c\sqrt[3]{4} \;|\; a,b,c \in \mathbb{Q}\}$, so one of
  its basis is $\{1 ,\sqrt[3]{2} ,\sqrt[3]{4}\}$, $p_\alpha = x^3 - 2$ and its degree
  is $3$.
\end{example}

\begin{theorem}
  [add font 45 p.40] If $K$ is a number field, then $K = \mathbb{Q}[\theta]$ for some
  algebraic number $\theta \in K$, called primitive element.
\end{theorem}

Then we conclude that \(\{1, \theta, \theta^2, ... , \theta^{n-1}\}\) is a basis for the vector
space \(K = \mathbb{Q}[\theta]\) over \(\mathbb{Q}\).

\section{Twisted Embedding}
\label{sec:org052db5b}

\chapter{Literature Review}
\label{sec:orgd36839f}

\chapter{Objectives Detailing}
\label{sec:org5eb7f60}

\chapter{Methodology}
\label{sec:orgf5dabcd}

\bibliographystyle{plain}
\bibliography{ic-tese-v3}
\end{document}